On the performance of the MAC model

### 2018-11-01 2018_nips_vigil/mac.tex
Vincent's changes

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting of attention over the image.
The core of the model is the MAC cell, supported with an input unit that processes question and image pair, and output unit which produces the answer.% (a two layer MLP).
The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
Besides, the input unit utilizes a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.

The MAC cell consists of a control unit, a read unit and a write unit (\Fig{fig:mac_cell}).
The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} $\cw$ taking into account the \emph{question representation} $q$.
Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $\kb$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state.

%The MAC network reached state-of-the-art accuracy on the CLEVR dataset.
%In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher computational efficiency and enhanced transparency.

%In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully differentiable and does not require additional supervision.

>>>>

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting the attention over the image.
The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
Besides, the input unit utilizes a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.

The MAC cell consists of a control unit, a read unit and a write unit (\Fig{fig:mac_cell}).
The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} $\cw$ taking into account the \emph{question representation} $q$.
Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $\kb$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state. Detailed equations are described in the next section.

### 2018-11-01 2018_nips_vigil/smac.tex
Shorteninf of MAC section, picked several experiment results from table 2
Vincent's changes

\subsection{Simplified MAC network}
Our proposed modification to the MAC network is based on two heuristic
simplifications of the MAC cell. 
First, we observe that when looking at the equations of different units
together as a whole, there are several linear layers
that are applied in sequence (with no activation in-between).
Therefore they can actually be combined to form a single linear layer.
The second observation uses the following heuristic assumption:
suppose there is an affine transformation that preserves the number
of dimensions. Then one can assume that the transformation is invertible
so as to avoid a loss in the information. Applying this principle to 
equations in the MAC cell results in eliminating one of the linear layers applied to
the knowledge base in the cell. With a careful reorganization, we in fact
can compute this operation on the knowledge base right after we apply the 2 
 CNN layers on the feature maps (i.e. prior to the reasoning steps). Thus, we can work purely
with this \emph{projected} knowledge base, that yields
noticeable savings in training time, as our experiments demonstrate
below, without incurring too much drop in accuracy.

In the description below, the original MAC cell equations are shown on the \emph{left}
while our simplified equations are shown (in color) on the {\color{Plum} \emph{right}}.
(The equation numbering is the same as in~\cite{hudson2018compositional}.)

>>>>

\subsection{Simplified MAC network}
Our proposed modification to the MAC network is based on two heuristic
simplifications of the MAC cell. 
First, we observe that when looking at the equations of different units
together as a whole, there are several linear layers
that are applied in sequence (with no activation in-between).
Therefore they can actually be combined to form a single linear layer.
The second observation is:
suppose there is an affine transformation that preserves the number
of dimensions. Then one can assume that the transformation is invertible
so as to avoid a loss in the information. Applying this principle to 
equations in the MAC cell results in eliminating one of the linear layers applied to
the knowledge base in the cell. With a careful reorganization, we
can compute this operation on the knowledge base right after we apply the 2 
 CNN layers on the feature maps (i.e. prior to the reasoning steps). Thus, we can work purely
with this \emph{projected} knowledge base, that yields
noticeable savings in training time, as our experiments demonstrate
below, without incurring too much drop in accuracy.

In the description below, the original MAC cell equations are shown on the \emph{left}
while our simplified equations are shown (in color) on the {\color{Plum} \emph{right}}.
The equation numbering is the same as in~\cite{hudson2018compositional}.
